A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-11 12_conclusions_future_work.tex
more conclusions

\begin{itemize}
\item Accurate filling using few/small overfill and underfill areas
\item Which allows for accurate reproduction of thin parts and variable thickness microstructures.
\item Our framework is able to emulate several previously proposed methods
\item Our framework allows for deposition width control which reduces the amount of extrusion paths with wildly different width compared to previous methods
\item Our framework allows for limiting the stretch on the outer toolpath in order to reduce any adverse affect of variable extrusion width on dimensional accuracy.
\item The computation times are approximately 3 times as fast as the state of the art method for naive toolpath generation employing constant width
\item (depending on what we do in the validation chapter) The produced parts employing our method are more stiff compared to other methods.
\end{itemize}

>>>>

\begin{itemize}
\item Accurate filling using few/small overfill and underfill areas
\item Which allows for accurate reproduction of thin parts and variable thickness microstructures.
\item Our framework is able to emulate several methods proposed in related literature.
\item Our framework allows for deposition width control which reduces the amount of extrusion paths with wildly different width compared to previous methods
\item Our framework allows for limiting the stretch on the outer toolpath in order to reduce any adverse affect of variable extrusion width on dimensional accuracy.
\item Our framework is stable against slight perturbations of the outline shape or large perturbations of the outline shape in far away regions.
\item We can define a strategy which distibutes the bead width deviation over a small region so as to retain smooth toolpaths of nominal width throughout the larger part of big regions.
\item Our strategy keep mechanical properties more constant.
\item The computation times are approximately 3(?) times as fast as the state of the art method for naive toolpath generation employing constant width.
\end{itemize}

### 2019-08-11 8_discussion.tex
more conclusions

\subsection{Theoretical analysis}
In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
The significance measure is an exact measure of the relative size of gaps when using the naive toolpathing method.
\todo{[figure showing wedges, naive toolpaths and gaps]}
Note also that contrary to some literature we don't remove bones from the skeleton, but leave it intact.
The final skeleton is still an exact and full feature descriptor.
In that sense our framework provides an exact solution space.

@@

\subsection{Comparison of different beading strategies}
\todo{Discussion of finding of Validation section}\

@@

>>>>

\subsection{Theoretical analysis}
In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
The significance measure is an exact measure of the relative size of gaps when using the naive toolpathing method.
See \cref{naive_overfill_underfill}
Note also that contrary to some literature we don't remove bones from the skeleton, but leave it intact.
The final skeleton is still an exact and full feature descriptor.
In that sense our framework provides an exact solution space.

@@

\subsection{Comparison of different beading strategies}
\todo{Discussion of finding of Validation section}

@@

\subsection{Computation time}
Algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$.
The number of elements in the trapezoidation is linear in the number of elements in the VD.
All of the stages of our framework are also linear in the number of elements in the skeleton.

Experiments.
The computation time is comparable to the naive method as implemented using Clipper.
